---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# basestats

![alt text](https://img.shields.io/badge/License-MIT-yellow.svg)

A collection of hypothesis test functions implemented in R, designed to be used directly as modules rather than a traditional package. This project focuses on providing clear implementations and demonstrating modular code organization with `box`.

## Overview

`basestats` provides recreations and potential extensions of common statistical hypothesis tests. Instead of bundling these into an R package, it leverages the `box` package for a modular approach. This allows users to directly use specific functions without installing a full package, promoting code transparency and easier modification.

The functions are currently organized, e.g. into parametric test functions (`par_funcs`) and non-parametric test functions (`npar_funcs`) categories.

## Dependencies

-   **`box`**: You can't use the function without `box` package installed in your system. This is the main requirement to use the modular functions in `basestats`.

    This is how you install the package:

    -   Installing this package from CRAN:

        ``` r
        install.packages('box')
        ```

    -   From R-universe:

        ``` r
        install.packages('box', repos = 'https://klmr.r-universe.dev')
        ```

    -   Or a development version:

        ``` r
        devtools::install_github("klmr/box")
        ```

-   **`tabhelpers`**: My newly created package, used for displaying formatted statistical outputs from a data frame or a matrix. Take note that this is still currently developing, so install this from GitHub:

    ``` r
    devtools::install_github("kisha126/tabhelpers")
    ```

-   **Core `tidyverse` packages (e.g., `dplyr`, `tidyr`)**: While the full `tidyverse` meta-package is convenient (`install.packages("tidyverse")`), the examples and potentially the `tabhelpers` package might rely specifically on packages like `dplyr` for data manipulation (e.g., using the `|>` pipe). Ensure relevant `tidyverse` components are installed.

-   R version must be \>4.2.0

## Project Structure

Here is the project structure:

```         
.
├── basestats
│   ├── __init__.R
│   ├── npar_funcs
│   │   ├── __init__.R
│   │   └── wilcoxtest.R
│   ├── par_funcs
│   │   ├── __init__.R
│   │   └── ttest.R
│   └── utils.R
├── README.md
└── README.rmd
```

*(Note: You'll need appropriate **init**.R files to export functions and sub-modules correctly for box::use)*

## Example Usage

Since `basestats` is not a package, but rather a structural directory, load the directory as a module with `bs` as an alias of it, and don't forget the `./` as the prefix. Ensure your R working directory is set correctly relative to the `basestats` directory. If `basestats` is a subdirectory of your current working directory, use `bs = ./basestats`.

```{r}
box::use(bs = ./basestats)
data("iris")

iris |> 
    bs$par$t_test(Sepal.Length, Sepal.Width, Petal.Length)

box::unload(bs)
```

## Contributing

[Optional: Add guidelines here if you welcome contributions, e.g., "Pull requests are welcome. For major changes, please open an issue first to discuss what you would like to change."]

## License

This project is licensed under the MIT License. See the [LICENSE](https://opensource.org/license/MIT) file or link for details.
